
Foremost, I would like to express my sincere gratitude to my thesis advisor Prof. Niladri Chatterjee (Department of Mathematics, IIT Delhi) and Raksha Agarwal (Research Scholar, Department of Mathematics, IIT Delhi) for their continuous guidance, constructive criticism and valuable suggestions throughout this project.
They consistently provided me with all the required resources for my work, encouraged me to follow my ideas and steered me in the right direction whenever they thought I needed it.
%. They also brought structure to both my research and thinking process and their expertise and knowledge has empowered me to deep dive and grow in this field of study. 

I thank the IIT Delhi HPC and the Google Colaboratory facilities for providing computational resources. I am grateful to Francisco Rangel et al., Valerio Basile et al. and Zeerak Waseem et al. for granting access to the datasets.


I would also like to take this opportunity to thank all my friends and teachers, whom I have met till now, for providing me with their unfailing support and continuous encouragement throughout the years. Last but not least, I am grateful to my parents for ensuring I always had everything I needed, especially in this difficult time. They have taught me always to put my best effort in all my endeavours and have consistently set this example for me to follow.


%%%%%%%%% BEFORE GRAMMARLY

% Foremost, I would like to express my sincere gratitude to my thesis advisor Prof. Niladri Chatterjee (Department of Mathematics, IIT Delhi) and Raksha Agarwal (Research Scholar, Department of Mathematics, IIT Delhi) for their continuous guidance, constructive criticism and valuable suggestions throughout the duration of this project.
% They consistently provided me with all the resources I required for my work, encouraged me to follow my ideas and steered me in the right the direction whenever they thought I needed it.
% % They also brought structure to both my research and thinking process, and their expertise and knowledge has empowered me to deep dive and grow in this field of study. 

% I also thank the IIT Delhi HPC and the Google Colaboratory facilities for providing with computational resources.


% I would also like to take this opportunity to thank all my friends and teachers whom I have met till now, for providing me with their unfailing support and continuous encouragement throughout the years. Last but not the least I am grateful to my parents in making sure I always had everything I needed, specially in this difficult time. They have taught me to always put my best effort in all my endevours and have consistently set this example for me to follow.

